\input{preamble_theme}

% ====================================================
% ====================================================
% BEGIN OF DOCUMENT
% ====================================================
% ====================================================
\begin{document}

\mytitle{Exercise 2 - Decision Theory and Density Estimation}
\myauthor{name1, name2, name3}
\firstpage{\insertmytitle}{Winter term 2019/2020}{\insertmyauthor}

% Bayesian Decision Theory
%______________________________________________________________________
\section{Bayesian Decision Theory}

\begin{enumerate}[label=\alph*)]

% Task 1
\exercise{Bayes' Rule (1 point)}{
State Bayes' rule and state the name of each term in the equation.
}{
\vspace*{7cm}
}




% Task 2
\exercise{Decision Boundary (1 point)}{
Which condition holds at the optimal decision boundary? In a binary classification problem, when do we prefer class $A$ over class $B$?
Why is it not necessary to normalize the probabilities on both sides of the inequality?
}{

}

\newpage


% Task 3
\exercise{Na\"ive Bayes (5 points)}{
You are planning a nice trip to the forest to collect some delicious mushrooms. However, you are not an expert for mushrooms and afraid of picking poisonous ones.
However, you have a data set called \cb{\texttt{mushrooms.csv}} describing the shape, color and habitat of different mushrooms and whether they are edible (type \textit{e}) or poisonous (type \textit{p}).
Implement a binary na\"ive Bayes classifier using \texttt{Python} and \texttt{numpy} / \texttt{pandas} and train it on the mushrooms data set. Use 10\,\% of the data set as test set and report your accuracy on this test set.
}{
\vspace*{7cm}
}




% Task 4
\exercise{Bonus Question (1 point)}{
You work for a machine learning startup which specializes in text classification for automatic scam detection in social networks. You are required by law to explain in detail why your system did not filter out content which was scam or why it did filter out normal content.
Given that both models are suitable, would you prefer a na\"ive Bayes model or a deep neural network? Why?
}{

}

\end{enumerate}

\newpage


% Density Estimation
%______________________________________________________________________
\section{Density Estimation}

\begin{enumerate}[label=\alph*)]

% Task 5
\exercise{Non-Parametric Density Estimation (3 points)}{
You want to estimate the density for the data stored in the file \cb{\texttt{density\_data\_train.csv}}. Implement either a kernel density estimator using a Gaussian kernel trying different values for $h$
\textbf{or} a $k$-nearest neighbors estimator trying different values for $k$. Which value for $h$ or $k$ works best? Plot the densities in a suitable interval.
}{

}

\end{enumerate}

\end{document}