% select theme
\input{../preamble_theme_2}

% ====================================================
% ====================================================
% OPTIONS
% ====================================================
% ====================================================

% number of levels in toc
\dwDeepToc{false}

% ====================================================
% ====================================================
% PRESENTATION DATA
% ====================================================
% ====================================================

\title[Introduction to Python for ML]{***** Introduction to Python for ML *****}
\author{Daniel Wehner, M.Sc.}
\institute[SAP\,SE]{SAP\,SE / DHBW Mannheim}
\date{Winter term 2020/2021}

% ====================================================
% ====================================================
% BEGIN OF DOCUMENT
% ====================================================
% ====================================================

\begin{document}

% Title frame
%______________________________________________________________________
\dwPrintTitle

% Agenda
%______________________________________________________________________
\dwPrintToc

% Section: Introduction
%______________________________________________________________________
\dwSection{Introduction}

% What is Python?
\begin{dwHeaderFrame}{What is Python?}
	\begin{itemize}
		\item Python was developed by Guido van Rossum in the early 1990s.
		\item It is an interpreted, high-level, general-purpose programming language which is the state-of-the-art for data science and machine learning.
		\item \textbf{White space has a meaning!} (important difference to other languages like Java or C++)
		\begin{itemize}
			\item Semantic code blocks (e.\,g. conditions, loops, ...) have to be indented.
			\item You may use tabs or spaces for indentation, but the interpreter \textbf{does not allow you to mix these two!}
		\end{itemize}
		\item Python supports many programming paradigms: We can write \textbf{procedural}, \textbf{functional} or \textbf{object-oriented} programs.
	\end{itemize}
\end{dwHeaderFrame}


\begin{frame}
	\begin{itemize}
		\item \textbf{Caveat:} Python has two \textbf{non-compatible} branches:
		\begin{itemize}
			\item \texttt{Python 2.7} $\Longleftarrow$ This one is deprecated and no longer maintained
			\item \texttt{Python 3.x} $\Longleftarrow$ Use this one!
		\end{itemize}
	\end{itemize}
\end{frame}


% Installation and Components
\begin{dwHeaderFrame}{Installation and Components}
	\dwHeader{Python}
	\begin{itemize}
		\item Python is pre-installed on Mac and Linux. You may check this by executing \texttt{python -V} in the command line.
		\item For Windows (and Mac), download the newst version from \externalurl{www.python.org/downloads/}{www.python.org/downloads/}.
		\item Don't forget to check the \texttt{`Add Python 3.x to PATH'} option!
	\end{itemize}
	\dwHeader{Jupyter}
	\begin{itemize}
		\item It is a browser-based Python environment (either on local or remote machine).
		\item The code is editable directly in the browser.
		\item Nice for (interactive) demonstrations, \textbf{but hard to debug}.
	\end{itemize}
\end{dwHeaderFrame}


\begin{frame}
	\dwHeader{Anaconda}
	\begin{itemize}
		\item A package manager for creating \textbf{isolated Python environments} (with different package versions)
		\item It is good programming practice to create separate environments for different projects in order to avoid version mismatches,
			package clashes etc.
		\item It can be downloaded from \externalurl{https://www.anaconda.com/download/}{https://www.anaconda.com/download/}
	\end{itemize}
	
	\dwInfoBox{I recommend to use the \textit{Anaconda Navigator} which combines all components, including a Python IDE called \textit{spyder}.}
\end{frame}


% Writing and running Python Scripts
\begin{dwHeaderFrame}{Writing and running Python Scripts}

\end{dwHeaderFrame}


\begin{frame}
	\lstinputlisting{00_intro_python/06_listings/test.txt}
\end{frame}


% Section: Data Types
%______________________________________________________________________
\dwSection{Data Types}

% Basic Data Types
\begin{dwHeaderFrame}{Basic Data Types}
	\begin{itemize}
		\item Unlike Java, Python is \textbf{typed dynamically}, i.\,e. the data type does not have to be specified when declaring variables.
		\item Nevertheless, Python works with these types internally (cf. \cref{tab:data_types}).
	\end{itemize}
	
	\input{00_intro_python/03_tbl/data_types}
\end{dwHeaderFrame}


\begin{frame}
	\dwHeader{Some examples}
	\lstinputlisting{00_intro_python/06_listings/data_types_string.txt}
\end{frame}


\begin{dwHeaderFrame}{Conversion between Types}
	\begin{itemize}
		\item Although you don't have to bother with types in Python, you may want to convert a variable to another type.
		\item E.\,g. when concatenating a number to a string
	\end{itemize}
	
	\lstinputlisting{00_intro_python/06_listings/type_conversion.txt}
\end{dwHeaderFrame}


% Thank you
%______________________________________________________________________
\makethanks

\end{document}
